---
title: "CH4"
author: 
Zhang Zhenglin
output:
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: sentence
---

# Necessary libraries

```{r message=FALSE,warning=FALSE}
library(knitr)
library(ggplot2)
theme_set(theme_bw())
library(emmeans)
library(multcomp)
library(PLS205)
library(lme4)
library(lmerTest)
library(multcompView)
library(car)
library(Rmisc) 
library(dplyr) #https://r4ds.had.co.nz/ (Chapter 3, Chapter 5, look at filter and select)
# https://bookdown.org/ansellbr/WEHI_tidyR_course_book/
library(stringr) 
library(data.table)
library(GGally)
library(formatR)
library(readxl)
library(FluxCalR)
library(tidyverse)
library(fuzzyjoin)
library(purrr)
library(data.table)
library(broom)
library(lubridate)
library(readxl)
library(openxlsx)
library(ggrepel)
library(gridExtra)
library(zoo)
library(writexl)
```

# Load data

```{r}
flux <- read_excel("../Data/Flux_Calc/Results/final_flux_input_results.xlsx", sheet = 1)
flux$Date <- as.Date(flux$Date)
str(flux)
```
# Add data from season start and end

```{r}
# 1) Remove the Plot 105 observation on 2025-09-09 (bad t=0 GC injection)
flux <- flux %>%
  filter(!(Plot == "105" & Date == as.Date("2025-09-09")))

# 2) First sampling event (2025-05-02) was recorded per-block (B1/B2/B3)
#    rather than per-plot. Allocate each block's flux to its 6 member plots.
block_lookup <- list(
  B1 = c("101", "102", "103", "104", "105", "106"),
  B2 = c("201", "202", "203", "204", "205", "206"),
  B3 = c("301", "302", "303", "304", "305", "306")
)

flux_block_rows <- flux %>%
  filter(Plot %in% names(block_lookup)) %>%
  rowwise() %>%
  mutate(Plot = list(block_lookup[[Plot]])) %>%
  unnest(Plot) %>%
  ungroup()

flux_other_rows <- flux %>%
  filter(!Plot %in% names(block_lookup))

flux <- bind_rows(flux_other_rows, flux_block_rows) %>%
  arrange(GC_Run, Date, Plot)

# 3) Add a CH4 = 0 end-of-season observation on 2025-09-24 for every plot
end_of_season <- tibble::tibble(
  Plot     = sort(unique(flux$Plot)),
  Date     = as.Date("2025-09-24"),
  CH4_Flux = 0
)

flux <- bind_rows(flux, end_of_season)
```

# Check total number of sampling events

```{r}
flux %>%
  summarise(n_dates = n_distinct(Date))
```

# Allocate plot to treatments

```{r}

flux <- flux %>%
mutate(Treatment = case_when(
  Plot %in% c("105", "201", "301") ~ "CF",
  Plot %in% c("106", "206", "302") ~ "CF-PP",
  Plot %in% c("101", "204", "306") ~ "LD",
  Plot %in% c("103", "205", "304") ~ "LD-PP",
  Plot %in% c("102", "203", "305") ~ "LD-MS",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  filter(Treatment != "Other") 

# 

#change to the right variable classes
flux$Plot <- as.factor(flux$Plot)
flux$Treatment <- as.factor(flux$Treatment)
flux$Date <- as.POSIXct(flux$Date)

#check that all variables look good
str(flux)
```

# Number of sampling events

```{r}
flux %>%
  summarise(n_dates = n_distinct(Date))
```

# Linear Interpolation

```{r}
flux_2025 <- flux %>%
  filter(Date >= as.POSIXct("2025-05-01") & Date <= as.POSIXct("2025-09-25")) %>%
  mutate(Treatment = case_when(
  Plot %in% c("105", "201", "301") ~ "CF",
  Plot %in% c("106", "206", "302") ~ "CF-PP",
  Plot %in% c("101", "204", "306") ~ "LD",
  Plot %in% c("103", "205", "304") ~ "LD-PP",
  Plot %in% c("102", "203", "305") ~ "LD-MS",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  filter(Treatment != "Other") %>%
  mutate(Drain = case_when(
  Plot %in% c("105", "201", "301") ~ "CF",
  Plot %in% c("106", "206", "302") ~ "CF",
  Plot %in% c("101", "204", "306") ~ "LD",
  Plot %in% c("103", "205", "304") ~ "LD",
  Plot %in% c("102", "203", "305") ~ "LD",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(Sulfate = case_when(
  Plot %in% c("105", "201", "301") ~ "0",
  Plot %in% c("106", "206", "302") ~ "300",
  Plot %in% c("101", "204", "306") ~ "0",
  Plot %in% c("103", "205", "304") ~ "300",
  Plot %in% c("102", "203", "305") ~ "350",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(Sulfate_logic = case_when(
  Plot %in% c("105", "201", "301") ~ "0",
  Plot %in% c("106", "206", "302") ~ "Yes",
  Plot %in% c("101", "204", "306") ~ "0",
  Plot %in% c("103", "205", "304") ~ "Yes",
  Plot %in% c("102", "203", "305") ~ "Yes",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(
    Blk = str_sub(as.character(Plot), 1, 1)
  )


start_date <- as.Date("2025-05-02")
end_date <- as.Date("2025-09-24")
date_seq <- seq.Date(start_date, end_date, by = "day")

flux_2025_rice_interpolated <- flux_2025 %>%
  group_by(Plot) %>%
  complete(Date = date_seq) %>%
  ungroup()

flux_2025_rice_interpolated <- flux_2025_rice_interpolated %>%
  group_by(Plot) %>%
  mutate(CH4_Flux = na.approx(CH4_Flux, rule = 2)) %>%
  mutate(CH4_flux_g_ha_day = CH4_Flux)%>%
  ungroup()

flux_2025_rice_seasonal_emissions <- flux_2025_rice_interpolated %>%
  group_by(Plot) %>%
  summarize(total_CH4_emissions = sum(CH4_flux_g_ha_day, na.rm = TRUE))%>% 
            #total_N2O_emissions = sum(N2O_g_ha_day, na.rm = TRUE)) 
  mutate(Period_Year = "Summer_2025") %>%
  mutate(Period = "Summer") %>%
  mutate(total_CH4_emissions_kg_ha = total_CH4_emissions/1000)%>%
  mutate(Treatment = case_when(
  Plot %in% c("105", "201", "301") ~ "CF",
  Plot %in% c("106", "206", "302") ~ "CF-PP",
  Plot %in% c("101", "204", "306") ~ "LD",
  Plot %in% c("103", "205", "304") ~ "LD-PP",
  Plot %in% c("102", "203", "305") ~ "LD-MS",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  filter(Treatment != "Other") %>%
  mutate(Drain = case_when(
  Plot %in% c("105", "201", "301") ~ "CF",
  Plot %in% c("106", "206", "302") ~ "CF",
  Plot %in% c("101", "204", "306") ~ "LD",
  Plot %in% c("103", "205", "304") ~ "LD",
  Plot %in% c("102", "203", "305") ~ "LD",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(Sulfate = case_when(
  Plot %in% c("105", "201", "301") ~ "0",
  Plot %in% c("106", "206", "302") ~ "300",
  Plot %in% c("101", "204", "306") ~ "0",
  Plot %in% c("103", "205", "304") ~ "300",
  Plot %in% c("102", "203", "305") ~ "350",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(Sulfate_logic = case_when(
  Plot %in% c("105", "201", "301") ~ "0",
  Plot %in% c("106", "206", "302") ~ "Yes",
  Plot %in% c("101", "204", "306") ~ "0",
  Plot %in% c("103", "205", "304") ~ "Yes",
  Plot %in% c("102", "203", "305") ~ "Yes",
  TRUE ~ "Other" # This line handles cases where plot is not listed
)) %>%
  mutate(
    Blk = str_sub(as.character(Plot), 1, 1)
  )


flux_2025_rice_seasonal_emissions$Drain <- as.factor(flux_2025_rice_seasonal_emissions$Drain)
flux_2025_rice_seasonal_emissions$Sulfate <- as.factor(flux_2025_rice_seasonal_emissions$Sulfate)
flux_2025_rice_seasonal_emissions$Sulfate_logic <- as.factor(flux_2025_rice_seasonal_emissions$Sulfate)

flux_2025_rice_seasonal_emissions$Treatment <- as.factor(flux_2025_rice_seasonal_emissions$Treatment)

ggplot(flux_2025_rice_interpolated, aes(y=CH4_flux_g_ha_day, x=Date, color = Plot)) + geom_point()
#ggplot(flux_2025_rice_interpolated, aes(y=N2O_g_ha_day, x=Date, color = Plot)) + geom_point()

write_xlsx(flux_2025_rice_seasonal_emissions, "../Data/seasonal_total_CH4.xlsx")


```

# Statistical tests

## Time-series 

```{r}
flux_2025 <- flux_2025 %>%  filter(Treatment !="LD-MS") 

model <- lmer(CH4_Flux~Drain*Sulfate+(1|Plot:Blk)+(1|Blk)+(1|Date), data=flux_2025) 
#specify co-variant structure 
#impose nested structure into the model
pls205_diagnostics(model)
anova(model)

Treatment_means <- emmeans(model, ~ Drain * Sulfate)

cld(Treatment_means,
    adjust = "tukey",
    Letters = letters)
```
## Cumulative CH4 

```{r}
# Remove LD-MS from the seasonal-emissions dataframe
flux_2025_rice_seasonal_emissions <- flux_2025_rice_seasonal_emissions %>%
  filter(Treatment != "LD-MS") %>%
  droplevels()

model_4trt <- lm(total_CH4_emissions_kg_ha ~ Sulfate*Drain, data = flux_2025_rice_seasonal_emissions)
anova(model_4trt)
pls205_diagnostics(model_4trt)

Treatment_means_4trt <- emmeans(model_4trt, spec = 'Drain', by = "Sulfate")
Treatment_effects_4trt <- contrast(Treatment_means_4trt, method = "pairwise", adjust = "tukey")
summary(Treatment_effects_4trt)
cld(Treatment_means_4trt, adjust = "tukey", Letters = letters)

cld_siddak <- cld(emmeans(Treatment_means_4trt, ~ Drain + Sulfate),adjust = "Sidak")
cld_siddak
```

# Plot CH4 over time

## Summarise data by data and treatment

```{r}
methane_all_graphing <- flux %>%
  group_by(Treatment, Date) %>%
  mutate(CH4_Flux_se = sd(CH4_Flux)/sqrt(n())) %>%
  summarise(CH4_Flux = mean(CH4_Flux),
  CH4_Flux_se = mean(CH4_Flux_se))
```

## Four treatments

```{r}
methane_all_graphing_4 <- methane_all_graphing %>% filter(Treatment !="LD-MS") 

methane_over_time_4 <- 
  ggplot(methane_all_graphing_4, aes(x = Date, y = CH4_Flux,  colour =  Treatment))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=CH4_Flux-CH4_Flux_se, ymax=CH4_Flux+CH4_Flux_se), size=0.5)+
  ggtitle("(a) Methane flux")+
  scale_x_datetime(name = "",
    limits = as.POSIXct(c("2025-05-01", "2025-09-25")), # Set x-axis limits
    date_labels = "%b",   # month only, no year
    date_breaks = "1 month")+
    scale_color_manual(
  values = c(
    "CF"   = "#3D6F73",
    "CF-PP" = "#86B7B8",
    "LD"   = "#A16E2A",
    "LD-PP" = "#D9B67A"
  ),
                     labels = c(expression("Continuous flood (CF)"), 
                                expression("Continuous flood and sulfate (CF-S)"),
                                expression("Mid-season drain (MD)"),
                                expression("Mid-season drain and sulfate (MD-S)")
                                )
                     )+
  labs(y = expression("Daily CH"[4]~"Flux (g ha"^-1~" day"^-1~")")) +
  theme_classic()+
  theme(axis.text.x = element_text(size=14, angle=0, hjust=0.5, vjust=1),
      axis.text.y = element_text(size=14),
      axis.title.y = element_text(size=16),
      plot.title = element_text(size=20, face="bold"),
      legend.text = element_text(size=14),
      legend.title = element_text(size=16, face="bold"),
      legend.key.size = unit(0.8, "cm"),
      legend.position = "bottom")+
  guides(colour = guide_legend(nrow = 2))+
# pre season sulfate    
  geom_vline(xintercept = as.POSIXct(c("2025-05-01")), 
             linetype = "dashed", color = "#5F8A8B") +
  geom_text(aes(x = as.POSIXct("2025-05-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) -600,
                label = "Pre-season sulfate"),
            angle = 90, vjust = -0.5, hjust = 0, color = "#5F8A8B", size =5) +
# Initial Flood    
  geom_vline(xintercept = as.POSIXct(c("2025-05-07")), 
             linetype = "dashed", color = "#5F8A8B") +
  geom_text(aes(x = as.POSIXct("2025-05-07"), 
                y = mean(CH4_Flux, na.rm = TRUE) -600,
                label = "Initial flood"),
            angle = 90, vjust = -0.5, hjust = 0, color = "#5F8A8B", size =5)    +
  
# Begin mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-06-21")), 
             linetype = "dashed", color = "#5F8A8B") +
  geom_text(aes(x = as.POSIXct("2025-06-21"), 
                y = mean(CH4_Flux, na.rm = TRUE) -600,
                label = "Drain start"),
            angle = 90, vjust = -0.5, hjust = 0, color = "#5F8A8B", size =5) +
  
# Reflood after mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-07-02")), 
             linetype = "dashed", color = "#5F8A8B") +
  geom_text(aes(x = as.POSIXct("2025-07-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) -600,
                label = "Drain end"),
            angle = 90, vjust = -0.5, hjust = 0, color = "#5F8A8B", size =5) +
# End of season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-09-07")), 
             linetype = "dashed", color = "#5F8A8B") +
  geom_text(aes(x = as.POSIXct("2025-09-07"), 
                y = mean(CH4_Flux, na.rm = TRUE) -600,
                label = "End of season drain"),
            angle = 90, vjust = -0.5, hjust = 0, color = "#5F8A8B", size =5) #+
  #geom_hline(yintercept = 0, linetype = "dashed", color = "grey40")
  
  
methane_over_time_4


ggsave(methane_over_time_4, filename = "../Figures/methane_over_time_4trt.jpg", height = 25, width = 30, units = "cm", dpi=400)
```





# Archival code

## All treatments

```{r}

methane_over_time <- 
  ggplot(methane_all_graphing, aes(x = Date, y = CH4_Flux,  colour =  Treatment))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=CH4_Flux-CH4_Flux_se, ymax=CH4_Flux+CH4_Flux_se), size=0.5)+
  ggtitle("Methane over time")+
  scale_x_datetime(name = "",
    limits = as.POSIXct(c("2025-05-01", "2025-09-11")), # Set x-axis limits
    date_labels = "%b %Y",
    date_breaks = "1 month")+
# pre season sulfate    
  geom_vline(xintercept = as.POSIXct(c("2025-05-01")), 
             linetype = "dashed", color = "red") +
  geom_text(aes(x = as.POSIXct("2025-05-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Pre-season sulfate"),
            angle = 90, vjust = -0.5, hjust = 0, color = "red", size =4) +

# mid season sulfate    
  geom_vline(xintercept = as.POSIXct(c("2025-07-01")), 
             linetype = "dashed", color = "red") +
  geom_text(aes(x = as.POSIXct("2025-07-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Mid-season sulfate"),
            angle = 90, vjust = 1.4, hjust = 0, color = "red", size =4)   +

# Initial Flood    
  geom_vline(xintercept = as.POSIXct(c("2025-05-07")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-05-07"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Initial flood"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4)    +
  
# Begin mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-06-21")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-06-21"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Drain start"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4) +
  
# Reflood after mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-07-01")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-07-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Drain end"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4) +

# Planting date
  geom_vline(xintercept = as.POSIXct(c("2025-05-10")), 
             linetype = "dashed", color = "darkgreen") +
  geom_text(aes(x = as.POSIXct("2025-05-10"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Planting"),
            angle = 90, vjust = -0.5, hjust = 0, color = "darkgreen", size =4)   
  
  
methane_over_time


ggsave(methane_over_time, filename = "../Figures/methane_over_time.jpg", height = 25, width = 30, units = "cm", dpi=400)
```

## Graph with soil sampling dates

```{r}
methane_over_time_soil_dates <- 
  ggplot(methane_all_graphing, aes(x = Date, y = CH4_Flux,  colour =  Treatment))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=CH4_Flux-CH4_Flux_se, ymax=CH4_Flux+CH4_Flux_se), size=0.5)+
  ggtitle("Methane over time")+
  scale_x_datetime(name = "",
    limits = as.POSIXct(c("2025-05-01", "2025-08-30")), # Set x-axis limits
    date_labels = "%b %Y",
    date_breaks = "1 month")+
# pre season sulfate    
  geom_vline(xintercept = as.POSIXct(c("2025-05-01")), 
             linetype = "dashed", color = "red") +
  geom_text(aes(x = as.POSIXct("2025-05-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Pre-season sulfate"),
            angle = 90, vjust = -0.5, hjust = 0, color = "red", size =4) +

# mid season sulfate    
  geom_vline(xintercept = as.POSIXct(c("2025-07-01")), 
             linetype = "dashed", color = "red") +
  geom_text(aes(x = as.POSIXct("2025-07-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Mid-season sulfate"),
            angle = 90, vjust = 1.4, hjust = 0, color = "red", size =4)   +

# Initial Flood    
  geom_vline(xintercept = as.POSIXct(c("2025-05-07")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-05-07"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Initial flood"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4)    +
  
# Begin mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-06-21")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-06-21"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Drain start"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4) +
  
# Reflood after mid season drain     
  geom_vline(xintercept = as.POSIXct(c("2025-07-01")), 
             linetype = "dashed", color = "blue") +
  geom_text(aes(x = as.POSIXct("2025-07-01"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Drain end"),
            angle = 90, vjust = -0.5, hjust = 0, color = "blue", size =4) +

# Planting date
  geom_vline(xintercept = as.POSIXct(c("2025-05-10")), 
             linetype = "dashed", color = "darkgreen") +
  geom_text(aes(x = as.POSIXct("2025-05-10"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Planting"),
            angle = 90, vjust = -0.5, hjust = 0, color = "darkgreen", size =4) +

# Soil sampling dates
  geom_vline(xintercept = as.POSIXct(c("2025-06-17")), 
             linetype = "dashed", color = "brown") +
  geom_text(aes(x = as.POSIXct("2025-06-17"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Pre Drain soils"),
            angle = 90, vjust = -0.5, hjust = 0, color = "brown", size =4)   +

  
  # Soil sampling dates
  geom_vline(xintercept = as.POSIXct(c("2025-07-14")), 
             linetype = "dashed", color = "brown") +
  geom_text(aes(x = as.POSIXct("2025-07-14"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Post Reflood soils"),
            angle = 90, vjust = -0.5, hjust = 0, color = "brown", size =4) +
 
   # Soil sampling dates
  geom_vline(xintercept = as.POSIXct(c("2025-08-19")), 
             linetype = "dashed", color = "brown") +
  geom_text(aes(x = as.POSIXct("2025-08-19"), 
                y = mean(CH4_Flux, na.rm = TRUE) * 1.05,
                label = "Late soils"),
            angle = 90, vjust = -0.5, hjust = 0, color = "brown", size =4) 
  
methane_over_time_soil_dates

ggsave(methane_over_time_soil_dates, filename = "../Figures/methane_over_time_soil_dates.jpg", height = 25, width = 30, units = "cm", dpi=400)
```


## Log transformation

```{r}
model <- lm(log(total_CH4_emissions_kg_ha)~Treatment, data=flux_2025_rice_seasonal_emissions)
anova(model)

pls205_diagnostics(model)

Treatment_means = emmeans(model,spec = 'Treatment')
Treatment_effects = contrast(Treatment_means, 
         method = "pairwise",
         adjust = "tukey")
summary(Treatment_effects)
cld(Treatment_means)

emmeans(model, ~ Treatment)


ggplot(flux_2025_rice_seasonal_emissions, aes(y=total_CH4_emissions_kg_ha, x=Treatment, color = Blk)) + geom_point()
```


```{r}
model <- lm(total_CH4_emissions_kg_ha~Treatment, data=flux_2025_rice_seasonal_emissions)
anova(model)

pls205_diagnostics(model)

Treatment_means = emmeans(model,spec = 'Treatment')
Treatment_effects = contrast(Treatment_means, 
         method = "pairwise",
         adjust = "tukey")
summary(Treatment_effects)
cld(Treatment_means)

emmeans(model, ~ Treatment)


ggplot(flux_2025_rice_seasonal_emissions, aes(y=total_CH4_emissions_kg_ha, x=Treatment, color = Treatment)) + geom_point()

```

# Anlyses for sulfate:drain interaction - very important 

```{r}
model <- lm(total_CH4_emissions_kg_ha~Drain*Sulfate, data=flux_2025_rice_seasonal_emissions)
anova(model)

Treatment_means = emmeans(model,spec = 'Drain', by = "Sulfate")
Treatment_effects = contrast(Treatment_means, method = 'pairwise', adjust = "tukey")
summary(Treatment_effects)
cld(Treatment_means)

emmeans(model, ~ Drain + Sulfate)
cld_siddak <- cld(emmeans(model, ~ Drain + Sulfate),adjust = "Sidak")
cld_siddak
# if we look at the summary output, sulfate = 350 has CF as not estimated. This is because the experiment is not a full 2x3 factorial design we probably have to play around with the linear model to account for that. 

ggplot(flux_2025_rice_seasonal_emissions, aes(y=total_CH4_emissions_kg_ha, x=Treatment, color = Treatment)) + geom_boxplot()

```
# Try without CF-PP

```{r}
model <- lm(log(total_CH4_emissions_kg_ha)~Sulfate*Drain, data=flux_2025_rice_seasonal_emissions%>%filter(Treatment !="LD-MS"))#%>%filter(Treatment !="CF-PP"))

pls205_diagnostics(model)
            
anova(model)



Treatment_means = emmeans(model,spec = 'Sulfate', by ='Drain')
Treatment_effects = contrast(Treatment_means, method = 'pairwise', adjust = "tukey")
summary(Treatment_effects)
cld(Treatment_means)


```
# Over time

```{r}
model <- lm(CH4_Flux~Treatment*as.factor(Date), data=flux_2025)
anova(model)

pls205_diagnostics(model)

Treatment_means = emmeans(model,spec = 'Treatment', by = 'Date')
Treatment_effects = contrast(Treatment_means, method = 'pairwise', adjust = "Tukey")
summary(Treatment_effects)
cld(Treatment_means)
```

