---
title: "VolCalc QC Walkthrough"
author: "Zhang"
output:
  html_document:
    toc: yes
    toc_float: yes
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
```

This document runs the flux calculation pipeline (`VolCalc_v2.R`'s logic) one file at a time, with a data-quality check printed after every stage. If something upstream broke, you should be able to see exactly where by scanning the tables top to bottom, instead of waiting for `VolCalc.R` to error out or silently hand back bad numbers.

Change `TARGET_FILE` below to point at whichever file in `ImportFiles/` you want to inspect. The last section runs the same logic over every *other* file in `ImportFiles/` without the chunk-by-chunk printing, so nothing is skipped — you just don't get the full QC dump for files you've already checked.

# 1. Setup

```{r libraries}
library(readxl)
library(writexl)
library(openxlsx)
library(dplyr)
library(knitr)

DETECTION_THRESHOLD   <- 0.000183
LINEARITY_R2_FULL     <- 0.845
LINEARITY_R2_FALLBACK <- 0.8545
FLUX_TIME_CONVERSION  <- 240 * 60
MOLAR_VOLUME_STP      <- 22.4     # L/mol at STP
CH4_MW                <- 0.016043 # g/mol
N2O_MW                <- 0.044014 # g/mol
CALIBRATION_R2_WARN   <- 0.95     # flag a batch's calibration if R^2 falls below this

BASE_DIR    <- "../Data/Flux_Calc"       # <-- matches your GC_Data_Wrangling.Rmd convention
TARGET_FILE <- "final_flux_input.xlsx"   # <-- change this to QC a different file

kable(data.frame(
  Constant = c("DETECTION_THRESHOLD","LINEARITY_R2_FULL","LINEARITY_R2_FALLBACK",
               "FLUX_TIME_CONVERSION","CALIBRATION_R2_WARN"),
  Value = c(DETECTION_THRESHOLD, LINEARITY_R2_FULL, LINEARITY_R2_FALLBACK,
            FLUX_TIME_CONVERSION, CALIBRATION_R2_WARN)
), caption = "Constants in effect for this run")
```

```{r fit-gas-function}
# Per-group gas fit: detection test + linearity test (with the original
# script's 4-point "drop one, keep best 3" fallback), generalized to use
# whichever Time values a group actually has.
fit_gas <- function(times, conc) {
  ok    <- !is.na(times) & !is.na(conc)
  times <- times[ok]
  conc  <- conc[ok]
  n     <- length(times)

  if (n < 2) {
    return(list(rsq = NA_real_, grad = NA_real_, lin = "MISSING", detect = "MISSING"))
  }

  o     <- order(times)
  times <- times[o]
  conc  <- conc[o]

  # PASS if ANY later point clears the threshold vs. the first
  # reading; NONDETECT only if every later point stays within it.
  # (Previously: any() single flat comparison zeroed the whole
  # group even when other points clearly showed a real change.)
  base   <- conc[1]
  detect <- if (any(abs(conc[-1] - base) >= DETECTION_THRESHOLD)) "PASS" else "NONDETECT"

  fit <- tryCatch(lm(conc ~ times), error = function(e) NULL)
  if (is.null(fit)) {
    return(list(rsq = NA_real_, grad = NA_real_, lin = "MISSING", detect = detect))
  }
  rsq  <- summary(fit)$r.squared
  grad <- unname(coef(fit)[2])

  lin <- "MISS"
  if (!is.na(rsq) && rsq > LINEARITY_R2_FULL) {
    lin <- "LIN"
  } else if (n == 4) {
    best_rsq <- -Inf
    best_grad <- grad
    for (drop in 1:4) {
      t3 <- times[-drop]
      c3 <- conc[-drop]
      f3 <- tryCatch(lm(c3 ~ t3), error = function(e) NULL)
      if (is.null(f3)) next
      r3 <- summary(f3)$r.squared
      if (!is.na(r3) && r3 > best_rsq) {
        best_rsq  <- r3
        best_grad <- unname(coef(f3)[2])
      }
    }
    if (is.finite(best_rsq) && best_rsq > LINEARITY_R2_FALLBACK) {
      lin  <- "LIN"
      rsq  <- best_rsq
      grad <- best_grad
    }
  }

  if (lin == "MISS")         grad <- 0
  if (detect == "NONDETECT") grad <- 0

  list(rsq = rsq, grad = grad, lin = lin, detect = detect)
}
```

# 2. Read the target file

```{r read-file}
filepath <- file.path(BASE_DIR, "ImportFiles", TARGET_FILE)
df <- read_excel(filepath)

if ("GC_Run " %in% names(df)) df <- df %>% dplyr::rename(GC_Run = `GC_Run `)
if ("Time "   %in% names(df)) df <- df %>% dplyr::rename(Time   = `Time `)
if (!"GC_Run" %in% names(df)) df$GC_Run <- TARGET_FILE

cat("File:", TARGET_FILE, "\n")
cat("Rows:", nrow(df), " Columns:", ncol(df), "\n")
kable(head(df, 5), caption = "First 5 rows as read")
```

## 2a. Data quality: missing values by column

**Check this before trusting anything downstream.** High `% NA` on `Chamber_Temp_C` or `Headspace*_cm` means those rows will drop out of the flux calc later; high `% NA` on `Std_*` means calibration will be starved for that batch.

```{r missing-value-audit}
na_summary <- data.frame(
  Column   = names(df),
  N_NA     = sapply(df, function(x) sum(is.na(x))),
  Pct_NA   = round(sapply(df, function(x) mean(is.na(x))) * 100, 1)
)
na_summary <- na_summary[order(-na_summary$Pct_NA), ]
kable(na_summary, row.names = FALSE, caption = "Missing values per column")
```

```{r sample-type-audit}
kable(as.data.frame(table(df$Sample_Type, useNA = "ifany")),
      col.names = c("Sample_Type", "N"),
      caption = "Row counts by Sample_Type")
```

# 3. Chamber volume / geometry

```{r geometry}
headspace_mean <- rowMeans(
  df[, c("Headspace1_cm", "Headspace2_cm", "Headspace3_cm", "Headspace4_cm")],
  na.rm = TRUE
)
extension_cm   <- df$Extension_ft * 30.48
chamber_Height <- extension_cm + 7.62 + headspace_mean
baseArea       <- pi * df$Chamber_Radius ^ 2
ChamberVolCm3  <- baseArea * chamber_Height
ChamberVolL    <- ChamberVolCm3 / 1000
BaseAreaM2     <- baseArea / 10000  # cm^2 -> m^2 (area, not volume -- was mislabeled "M3" in the original script)
VolAreaRatio   <- ChamberVolL / BaseAreaM2

df$HeadspaceMean_cm <- headspace_mean
df$Extension_cm     <- extension_cm
df$Chamber_Height   <- chamber_Height
df$Total_Volume_cm3 <- ChamberVolCm3
df$Total_Volume_L   <- ChamberVolL
df$Base_Area        <- baseArea
df$Base_Area_m2     <- BaseAreaM2
df$VolumeRatio      <- VolAreaRatio
```

## 3a. Data quality: geometry sanity checks

A negative or zero `Chamber_Height`/`VolumeRatio` means a headspace or radius value is wrong (or missing) for that row — worth fixing before flux calc, not after.

```{r geometry-audit}
geom_summary <- data.frame(
  Metric = c("Chamber_Height", "VolumeRatio", "Chamber_Radius"),
  Min    = c(min(chamber_Height, na.rm=TRUE), min(VolAreaRatio, na.rm=TRUE), min(df$Chamber_Radius, na.rm=TRUE)),
  Median = c(median(chamber_Height, na.rm=TRUE), median(VolAreaRatio, na.rm=TRUE), median(df$Chamber_Radius, na.rm=TRUE)),
  Max    = c(max(chamber_Height, na.rm=TRUE), max(VolAreaRatio, na.rm=TRUE), max(df$Chamber_Radius, na.rm=TRUE)),
  N_NA   = c(sum(is.na(chamber_Height)), sum(is.na(VolAreaRatio)), sum(is.na(df$Chamber_Radius))),
  N_LE_0 = c(sum(chamber_Height <= 0, na.rm=TRUE), sum(VolAreaRatio <= 0, na.rm=TRUE), sum(df$Chamber_Radius <= 0, na.rm=TRUE))
)
kable(geom_summary, caption = "Geometry ranges — check N_LE_0 is 0")

bad_geom <- df[which(chamber_Height <= 0 | VolAreaRatio <= 0), c("GC_Run","Plot","Date","Time")]
if (nrow(bad_geom) > 0) {
  kable(bad_geom, caption = "Rows with non-positive chamber height/volume ratio — REVIEW")
} else {
  cat("OK: no rows with non-positive chamber height or volume ratio.\n")
}
```

# 4. Per-batch (GC_Run) calibration

This is the most important QC table in the whole document — **one row per batch**, so you can immediately see which batches have weak standards before they quietly poison that batch's flux numbers.

```{r calibration}
df$CH4_Output <- NA_real_
df$N2O_Output <- NA_real_

batches <- unique(df$GC_Run)
calib_report <- vector("list", length(batches))

for (i in seq_along(batches)) {
  b <- batches[i]
  rows_b <- which(df$GC_Run == b)

  std_ch4 <- df[rows_b, ]
  std_ch4 <- std_ch4[!is.na(std_ch4$Std_CH4_Peak) & !is.na(std_ch4$Std_CH4_PPM), ]
  n_ch4 <- nrow(std_ch4)
  ch4_r2 <- NA_real_; ch4_slope <- NA_real_
  if (n_ch4 >= 2) {
    CH4model  <- lm(Std_CH4_PPM ~ Std_CH4_Peak, data = std_ch4)
    ch4_r2    <- summary(CH4model)$r.squared
    ch4_slope <- unname(coef(CH4model)[2])
    ch4_c     <- unname(coef(CH4model)[1])
    idx <- rows_b[!is.na(df$CH4_Sample_Peak[rows_b])]
    df$CH4_Output[idx] <- ch4_slope * df$CH4_Sample_Peak[idx] + ch4_c
  }

  std_n2o <- df[rows_b, ]
  std_n2o <- std_n2o[!is.na(std_n2o$Std_N2O_Peak) & !is.na(std_n2o$Std_N2O_PPM), ]
  n_n2o <- nrow(std_n2o)
  n2o_r2 <- NA_real_; n2o_slope <- NA_real_
  if (n_n2o >= 2) {
    N2Omodel  <- lm(Std_N2O_PPM ~ Std_N2O_Peak, data = std_n2o)
    n2o_r2    <- summary(N2Omodel)$r.squared
    n2o_slope <- unname(coef(N2Omodel)[2])
    n2o_c     <- unname(coef(N2Omodel)[1])
    idx <- rows_b[!is.na(df$N2O_Sample_Peak[rows_b])]
    df$N2O_Output[idx] <- n2o_slope * df$N2O_Sample_Peak[idx] + n2o_c
  }

  std_names_present <- unique(na.omit(df$standard_name[rows_b]))
  # standard_name may not exist if this file predates that column
  required <- c("1N500", "10M", "10N", "ambient")
  missing_types <- if ("standard_name" %in% names(df)) setdiff(required, std_names_present) else NA

  calib_report[[i]] <- data.frame(
    GC_Run         = b,
    N_CH4_Std      = n_ch4,
    CH4_Slope      = ch4_slope,
    CH4_R2         = ch4_r2,
    N_N2O_Std      = n_n2o,
    N2O_Slope      = n2o_slope,
    N2O_R2         = n2o_r2,
    Missing_Std_Types = if (length(missing_types) == 0 || (length(missing_types)==1 && is.na(missing_types))) "" else paste(missing_types, collapse=", "),
    Flag           = ""
  )
}

calib_report <- bind_rows(calib_report)
calib_report$Flag <- with(calib_report, ifelse(
  N_CH4_Std < 2 | N_N2O_Std < 2, "CHECK: <2 standards",
  ifelse(!is.na(CH4_R2) & CH4_R2 < CALIBRATION_R2_WARN, paste0("CHECK: CH4 R2=", round(CH4_R2,3)),
  ifelse(!is.na(N2O_R2) & N2O_R2 < CALIBRATION_R2_WARN, paste0("CHECK: N2O R2=", round(N2O_R2,3)),
  ifelse(Missing_Std_Types != "", paste0("CHECK: missing ", Missing_Std_Types), "OK")))
))

kable(calib_report, digits = 5, row.names = FALSE, caption = "Per-batch calibration summary")

n_flagged <- sum(calib_report$Flag != "OK")
if (n_flagged > 0) {
  cat("\n", n_flagged, "of", nrow(calib_report), "batches flagged for review (see Flag column above).\n")
} else {
  cat("\nOK: every batch has >=2 standards for each gas, R^2 >=", CALIBRATION_R2_WARN, ", and all 4 standard types present.\n")
}
```

## 4a. Calibration curves (visual check)

```{r calibration-plots, fig.width=5, fig.height=4}
for (b in batches) {
  rows_b <- which(df$GC_Run == b)
  std_ch4 <- df[rows_b, ]
  std_ch4 <- std_ch4[!is.na(std_ch4$Std_CH4_Peak) & !is.na(std_ch4$Std_CH4_PPM), ]
  if (nrow(std_ch4) >= 2) {
    plot(std_ch4$Std_CH4_Peak, std_ch4$Std_CH4_PPM, type = "o",
         xlab = "CH4 Peak", ylab = "CH4 PPM", main = paste0(b, " — CH4 Calibration"))
  }
}
for (b in batches) {
  rows_b <- which(df$GC_Run == b)
  std_n2o <- df[rows_b, ]
  std_n2o <- std_n2o[!is.na(std_n2o$Std_N2O_Peak) & !is.na(std_n2o$Std_N2O_PPM), ]
  if (nrow(std_n2o) >= 2) {
    plot(std_n2o$Std_N2O_Peak, std_n2o$Std_N2O_PPM, type = "o",
         xlab = "N2O Peak", ylab = "N2O PPM", main = paste0(b, " — N2O Calibration"))
  }
}
```

# 5. Concentration conversion

```{r concentration}
N2O_Vol <- (760 * MOLAR_VOLUME_STP * (273 + df$Chamber_Temp_C)) / (760 * 273)
df$N2O_Volume        <- N2O_Vol
df$N2O_Concentration <- df$N2O_Output / N2O_Vol * N2O_MW

CH4_Vol <- (760 * MOLAR_VOLUME_STP * (273 + df$Chamber_Temp_C)) / (760 * 273)
df$CH4_Volume        <- CH4_Vol
df$CH4_Concentration <- df$CH4_Output / CH4_Vol * CH4_MW
```

## 5a. Data quality: concentration output

```{r concentration-audit}
sample_rows <- df[df$Sample_Type == "Sample", ]
conc_summary <- data.frame(
  Column = c("CH4_Concentration", "N2O_Concentration"),
  N          = nrow(sample_rows),
  N_NA       = c(sum(is.na(sample_rows$CH4_Concentration)), sum(is.na(sample_rows$N2O_Concentration))),
  Pct_NA     = round(c(mean(is.na(sample_rows$CH4_Concentration)), mean(is.na(sample_rows$N2O_Concentration))) * 100, 1),
  Median     = c(median(sample_rows$CH4_Concentration, na.rm=TRUE), median(sample_rows$N2O_Concentration, na.rm=TRUE)),
  Max        = c(max(sample_rows$CH4_Concentration, na.rm=TRUE), max(sample_rows$N2O_Concentration, na.rm=TRUE))
)
kable(conc_summary, digits = 6, caption = "Concentration summary (Sample rows only)")

if (any(conc_summary$Pct_NA > 0)) {
  cat("\nSample rows missing a concentration (usually a missing Chamber_Temp_C or a batch with <2 standards):\n")
  missing_rows <- sample_rows[is.na(sample_rows$CH4_Concentration) | is.na(sample_rows$N2O_Concentration),
                               c("GC_Run","Plot","Date","Time","Chamber_Temp_C")]
  kable(head(missing_rows, 20), caption = "First 20 affected rows")
}
```

# 6. Flux calculation

Grouped by (GC_Run, Plot, Date), fit against each group's **actual** Time values — not a hardcoded 0/21/42/63.

```{r flux-groups}
flux_data <- df %>%
  dplyr::filter(!is.na(Plot)) %>%
  dplyr::select(GC_Run, Plot, Date, Time, N2O_Concentration, CH4_Concentration, VolumeRatio)

group_keys <- flux_data %>% dplyr::distinct(GC_Run, Plot, Date)
cat("Total (GC_Run, Plot, Date) groups to fit:", nrow(group_keys), "\n")

results <- vector("list", nrow(group_keys))

for (i in seq_len(nrow(group_keys))) {
  key <- group_keys[i, ]
  rows_g <- flux_data %>%
    dplyr::filter(
      GC_Run == key$GC_Run,
      Plot   == key$Plot,
      (is.na(Date) & is.na(key$Date)) | (!is.na(Date) & !is.na(key$Date) & Date == key$Date)
    )

  volumeratio <- rows_g$VolumeRatio[1]
  n2o_fit <- fit_gas(rows_g$Time, rows_g$N2O_Concentration)
  ch4_fit <- fit_gas(rows_g$Time, rows_g$CH4_Concentration)

  n2o_flux <- if (is.na(n2o_fit$grad) || is.na(volumeratio)) NA_real_ else n2o_fit$grad * volumeratio * FLUX_TIME_CONVERSION
  ch4_flux <- if (is.na(ch4_fit$grad) || is.na(volumeratio)) NA_real_ else ch4_fit$grad * volumeratio * FLUX_TIME_CONVERSION

  results[[i]] <- data.frame(
    GC_Run        = key$GC_Run,
    Plot          = key$Plot,
    Date          = format(key$Date),
    N_points      = nrow(rows_g),
    N20Detection  = n2o_fit$detect,
    CH4Detection  = ch4_fit$detect,
    N20_Rsq       = n2o_fit$rsq,
    CH4_Rsq       = ch4_fit$rsq,
    N20_Linearity = n2o_fit$lin,
    CH4_Linearity = ch4_fit$lin,
    N20_Slope     = n2o_fit$grad,
    CH4_Slope     = ch4_fit$grad,
    N20_Flux      = n2o_flux,
    CH4_Flux      = ch4_flux,
    stringsAsFactors = FALSE
  )
}
results <- bind_rows(results)
```

## 6a. Data quality: group sizes

Every group should have exactly 4 points unless you know a plot was sampled on a different schedule. Anything else is worth a second look.

```{r group-size-audit}
kable(as.data.frame(table(results$N_points)),
      col.names = c("N_points_in_group", "N_groups"),
      caption = "Distribution of points per (GC_Run, Plot, Date) group")

odd_groups <- results[results$N_points != 4, c("GC_Run","Plot","Date","N_points")]
if (nrow(odd_groups) > 0) {
  kable(odd_groups, caption = "Groups without exactly 4 points — confirm these are real (e.g. a different sampling protocol), not a merge gap")
} else {
  cat("OK: every group has exactly 4 points.\n")
}
```

## 6b. Data quality: detection / linearity outcome

**This is the table to check before trusting any CH4_Flux/N20_Flux number.** A flux of 0 could mean "PASS + LIN, true zero slope" or "NONDETECT" or "MISS" — this breaks that down so 0 isn't a black box.

```{r detection-audit}
kable(as.data.frame(table(CH4 = results$CH4Detection, useNA = "ifany")),
      col.names = c("CH4Detection", "N"), caption = "CH4 detection outcome")
kable(as.data.frame(table(N2O = results$N20Detection, useNA = "ifany")),
      col.names = c("N20Detection", "N"), caption = "N2O detection outcome")
kable(as.data.frame(table(CH4 = results$CH4_Linearity, useNA = "ifany")),
      col.names = c("CH4_Linearity", "N"), caption = "CH4 linearity outcome")
kable(as.data.frame(table(N2O = results$N20_Linearity, useNA = "ifany")),
      col.names = c("N20_Linearity", "N"), caption = "N2O linearity outcome")

missing_groups <- results[results$CH4Detection == "MISSING" | results$N20Detection == "MISSING",
                           c("GC_Run","Plot","Date","N_points")]
if (nrow(missing_groups) > 0) {
  kable(missing_groups, caption = "Groups marked MISSING (fewer than 2 usable concentration points) — REVIEW")
} else {
  cat("OK: no groups marked MISSING.\n")
}
```

## 6c. Flux summary

```{r flux-summary}
flux_summary <- data.frame(
  Gas       = c("CH4_Flux", "N20_Flux"),
  N         = nrow(results),
  N_NA      = c(sum(is.na(results$CH4_Flux)), sum(is.na(results$N20_Flux))),
  N_zero    = c(sum(results$CH4_Flux == 0, na.rm=TRUE), sum(results$N20_Flux == 0, na.rm=TRUE)),
  N_nonzero = c(sum(results$CH4_Flux != 0, na.rm=TRUE), sum(results$N20_Flux != 0, na.rm=TRUE)),
  Median_nonzero = c(median(results$CH4_Flux[results$CH4_Flux != 0], na.rm=TRUE),
                      median(results$N20_Flux[results$N20_Flux != 0], na.rm=TRUE))
)
kable(flux_summary, digits = 6, caption = "Flux outcome summary")

kable(head(results, 10), digits = 6, caption = "First 10 result rows")
```

# 7. Export this file's results

```{r export-target}
dir.create(file.path(BASE_DIR, "Results"), showWarnings = FALSE)
out_name <- paste0(tools::file_path_sans_ext(TARGET_FILE), "_results.xlsx")
write_xlsx(results, file.path(BASE_DIR, "Results", out_name))
cat("Wrote", nrow(results), "rows to", file.path(BASE_DIR, "Results", out_name), "\n")
```

# 8. Run the rest of ImportFiles/ (no per-chunk QC)

Same logic as above, applied to every other `.xlsx` file in `ImportFiles/`, so nothing gets left out just because you're only spot-checking `TARGET_FILE` above. Each file still gets its own printed one-line summary so you can tell at a glance if any of them need the full walkthrough treatment too.

```{r batch-rest}
all_files <- list.files(path = file.path(BASE_DIR, "ImportFiles"))
all_files <- all_files[grepl("\\.xlsx$", all_files) & !startsWith(all_files, "~$")]
other_files <- setdiff(all_files, TARGET_FILE)

run_one_file <- function(rowname) {
  filepath <- file.path(BASE_DIR, "ImportFiles", rowname)
  df <- read_excel(filepath)
  if ("GC_Run " %in% names(df)) df <- df %>% dplyr::rename(GC_Run = `GC_Run `)
  if ("Time "   %in% names(df)) df <- df %>% dplyr::rename(Time   = `Time `)
  if (!"GC_Run" %in% names(df)) df$GC_Run <- rowname

  headspace_mean <- rowMeans(df[, c("Headspace1_cm","Headspace2_cm","Headspace3_cm","Headspace4_cm")], na.rm = TRUE)
  df$VolumeRatio <- ((pi * df$Chamber_Radius^2) * (df$Extension_ft*30.48 + 7.62 + headspace_mean) / 1000) /
                     ((pi * df$Chamber_Radius^2) / 10000)

  df$CH4_Output <- NA_real_
  df$N2O_Output <- NA_real_
  for (b in unique(df$GC_Run)) {
    rows_b <- which(df$GC_Run == b)
    std_ch4 <- df[rows_b, ]; std_ch4 <- std_ch4[!is.na(std_ch4$Std_CH4_Peak) & !is.na(std_ch4$Std_CH4_PPM), ]
    if (nrow(std_ch4) >= 2) {
      m <- lm(Std_CH4_PPM ~ Std_CH4_Peak, data = std_ch4)
      idx <- rows_b[!is.na(df$CH4_Sample_Peak[rows_b])]
      df$CH4_Output[idx] <- unname(coef(m)[2]) * df$CH4_Sample_Peak[idx] + unname(coef(m)[1])
    }
    std_n2o <- df[rows_b, ]; std_n2o <- std_n2o[!is.na(std_n2o$Std_N2O_Peak) & !is.na(std_n2o$Std_N2O_PPM), ]
    if (nrow(std_n2o) >= 2) {
      m2 <- lm(Std_N2O_PPM ~ Std_N2O_Peak, data = std_n2o)
      idx <- rows_b[!is.na(df$N2O_Sample_Peak[rows_b])]
      df$N2O_Output[idx] <- unname(coef(m2)[2]) * df$N2O_Sample_Peak[idx] + unname(coef(m2)[1])
    }
  }

  N2O_Vol <- (760 * MOLAR_VOLUME_STP * (273 + df$Chamber_Temp_C)) / (760 * 273)
  df$N2O_Concentration <- df$N2O_Output / N2O_Vol * N2O_MW
  CH4_Vol <- (760 * MOLAR_VOLUME_STP * (273 + df$Chamber_Temp_C)) / (760 * 273)
  df$CH4_Concentration <- df$CH4_Output / CH4_Vol * CH4_MW

  flux_data <- df %>% dplyr::filter(!is.na(Plot)) %>%
    dplyr::select(GC_Run, Plot, Date, Time, N2O_Concentration, CH4_Concentration, VolumeRatio)
  group_keys <- flux_data %>% dplyr::distinct(GC_Run, Plot, Date)

  rows_out <- vector("list", nrow(group_keys))
  for (i in seq_len(nrow(group_keys))) {
    key <- group_keys[i, ]
    rows_g <- flux_data %>% dplyr::filter(
      GC_Run == key$GC_Run, Plot == key$Plot,
      (is.na(Date) & is.na(key$Date)) | (!is.na(Date) & !is.na(key$Date) & Date == key$Date)
    )
    volumeratio <- rows_g$VolumeRatio[1]
    n2o_fit <- fit_gas(rows_g$Time, rows_g$N2O_Concentration)
    ch4_fit <- fit_gas(rows_g$Time, rows_g$CH4_Concentration)
    n2o_flux <- if (is.na(n2o_fit$grad) || is.na(volumeratio)) NA_real_ else n2o_fit$grad * volumeratio * FLUX_TIME_CONVERSION
    ch4_flux <- if (is.na(ch4_fit$grad) || is.na(volumeratio)) NA_real_ else ch4_fit$grad * volumeratio * FLUX_TIME_CONVERSION
    rows_out[[i]] <- data.frame(
      GC_Run = key$GC_Run, Plot = key$Plot, Date = format(key$Date), N_points = nrow(rows_g),
      N20Detection = n2o_fit$detect, CH4Detection = ch4_fit$detect,
      N20_Rsq = n2o_fit$rsq, CH4_Rsq = ch4_fit$rsq,
      N20_Linearity = n2o_fit$lin, CH4_Linearity = ch4_fit$lin,
      N20_Slope = n2o_fit$grad, CH4_Slope = ch4_fit$grad,
      N20_Flux = n2o_flux, CH4_Flux = ch4_flux, stringsAsFactors = FALSE
    )
  }
  bind_rows(rows_out)
}

if (length(other_files) == 0) {
  cat("No other files to process — TARGET_FILE was the only one in ImportFiles/.\n")
} else {
  for (f in other_files) {
    res <- run_one_file(f)
    out_name <- paste0(tools::file_path_sans_ext(f), "_results.xlsx")
    write_xlsx(res, file.path(BASE_DIR, "Results", out_name))
    cat(sprintf(
      "%-30s groups=%-4d CH4 nondetect=%-4d N2O nondetect=%-4d missing=%-4d -> %s\n",
      f, nrow(res),
      sum(res$CH4Detection == "NONDETECT", na.rm=TRUE),
      sum(res$N20Detection == "NONDETECT", na.rm=TRUE),
      sum(res$CH4Detection == "MISSING" | res$N20Detection == "MISSING", na.rm=TRUE),
      out_name
    ))
  }
}
```
